Generalised gravitational burst searches with Generative Adverserial Networks~\chris{Need to change the title if we don't search}

### 2020-03-05 Paper_draft/GAN_paper.tex
Update GAN_paper.tex

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{acronym}
\usepackage{comment}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\begin{itemize}
\item Need to introduce GWs - the current state of the field e.g. detections
and LVC papers
\item Introduce burst searches - what's the point of burst searches - lots of references
\item Discuss the family of burst waveforms currently used and why - not in detail, just
an introduction
\item Introduce ML techniques in GWs - lots of references
\item What this paper does on GANs in 1 paragraph
\item Describe the structure of the paper 
\end{itemize}

@@

\begin{itemize}
\item Describe GANs in detail but really focus on the fact that the reader is a
GW data analyst - not a computer scientist
\item A diagram would be very useful
\item Do not discuss our specific case here - just stay general
\item A subsection on the specific advanced flavour of GAN that you are using
here - motivate this choice.
\end{itemize}

Generative adversarial networks (GANs) have seen considerable success in recent
years as a generative machine learning model. GANs work to train two competing
neural networks, consisting of a discriminator D that is trained to distinguish
between real and fake data and a generator G that produces synthetic
reproductions of the real data. The original GAN method has G perform a mapping
from an input noise vector z to its representation of the data and D maps its
input x to a probability [0,1] that the input came form either the training
data or G. Both networks compete in turn to trick the other and after training,
G produces accurate distributions and D can detect forgeries. During training,
D s given a batch of samples that contains one half real data (labelled as 1)
and one half fake data (labelled as 0) which it then makes predictions on. The
loss on D is calculated by comparing its predictions to the labels through a
defined loss function. (talk about binary cross entropy). The training process
of a GAN alternatively updates the weights of the D and G based on information
on its competitors loss function. This loss of D is used to update the weights
of G to produce more realistic samples of the input distribution, the loss of G
encourages the D to update its classification abilities. Both networks compete
in a minimax game that is tied to a value function V (D, G) which G is trying
minimise and D is trying to maximise:

\begin{multline}
\mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\bold{x} \sim p_{\text{r}}(\bold{x})} [\text{log} D(\bold{x})] \\ + \mathbb{E}_{\bold{z} \sim p_{\text{z}}(\bold{z})} [\text{log}(1-D(G(\bold{z})))]
\label{equation:GANloss}
\end{multline}

In theory this will eventually lead to the local Nash equilibrium [18] where
both neural networks are trained optimally. In practice, however, GANs are
notoriously difficult to train. Such difficulties include: Non-convergence,
where the model parameters oscillate and the loss never converges. Mode
collapse where G produces a limited diversity of samples, and the diminishing
gradient problem when applying the gradient descent algorithm to a
non-continuous function.  \\ To overcome some of these difficulties [blank]
proposed adding structure to the latent space by providing G with a class
label. This has the effect of making a point in latent space conditional on a
provided class. [blank] extends this idea further by requiring D to output a
probability of the data belonging to each class.

@@

@@

>>>>

\usepackage[draft]{graphicx}% Include figure files
\graphicspath{images}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{acronym}
\usepackage{comment}
\usepackage{standalone}
\usepackage{tikz}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{pifont}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\begin{comment}

\begin{itemize}
\item Need to introduce GWs - the current state of the field e.g. detections
and LVC papers
\item Introduce burst searches - what's the point of burst searches - lots of references
\item Discuss the family of burst waveforms currently used and why - not in detail, just
an introduction
\item Introduce ML techniques in GWs - lots of references
\item What this paper does on GANs in 1 paragraph
\item Describe the structure of the paper 
\end{itemize}
\end{comment}

@@

\begin{comment}
\begin{itemize}
\item Describe GANs in detail but really focus on the fact that the reader is a
GW data analyst - not a computer scientist
\item A diagram would be very useful
\item Do not discuss our specific case here - just stay general
\item A subsection on the specific advanced flavour of GAN that you are using
here - motivate this choice.
\end{itemize}
\end{comment}

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.45\columnwidth}
        \centering
        \input{GAN_diagram_vertical}%     without .tex extension
        \caption{Vanilla GAN}
        \label{fig:GAN}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.55\columnwidth}
        \centering
        \input{ACGAN_diagram_vertical}%     without .tex extension
        \caption{AC-GAN}
        \label{fig:ACGAN}
    \end{subfigure}\hfill
    \caption{Comparison of the original GAN method and the Auxiliary Conditional-GAN method }
\end{figure}

Generative adversarial networks (GANs) have seen considerable success in recent
years as a generative machine learning model. GANs work to train two competing
neural networks, consisting of a discriminator \textbf{D} that is trained to distinguish
between real and fake data and a generator \textbf{G} that produces synthetic
reproductions of the real data. The GAN method has \textbf{G} perform a mapping
from an input noise vector \textbf{z} to its representation of the data and \textbf{D} maps its
input \textbf{x} to a probability that the input came form either the training
data or \textbf{G}.  During training, \textbf{D} is given a batch of samples that contains one half real data (labelled as 1)
and one half fake data (labelled as 0) which it then makes predictions on. The
loss for \textbf{D} is calculated by comparing its predictions to the labelled data through the binary cross-entropy function. The training process
of a GAN alternatively updates the weights of the \textbf{D} and \textbf{G} based on information
on its competitors loss function. This loss of \textbf{D} is used to update the weights
of \textbf{G} to produce more realistic samples of the input distribution, the loss of G
encourages \textbf{D} to update its classification abilities. Both networks compete
in a minimax game that is tied to a value function V (D, G) which \textbf{G} is trying
minimise and \textbf{D} is trying to maximise:

\begin{multline}
\mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\bold{x} \sim p_{\text{r}}(\bold{x})} [\text{log} D(\bold{x})] \\ + \mathbb{E}_{\bold{z} \sim p_{\text{z}}(\bold{z})} [\text{log}(1-D(G(\bold{z})))]
\label{equation:GANloss}
\end{multline}
\subsection{Auxiliary conditional GANs}
In theory this will eventually lead to the local Nash equilibrium [18] where
both neural networks are trained optimally. In practice, however, GANs are
notoriously difficult to train. Such difficulties include: Non-convergence,
where the model parameters oscillate and the loss never converges. Mode
collapse where G produces a limited diversity of samples, and the diminishing
gradient problem when applying gradient descent to a
non-continuous function.  \\ To overcome some of these difficulties [blank]
proposed adding structure to the latent space by providing G with a class
label. This has the effect of making a point in latent space conditional on a
provided class. [blank] extends this idea further by requiring D to output a
probability of the data belonging to each class.

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.1]{images/real_fake_sample.png}
    \caption{Caption}
    \label{fig:my_label}
\end{figure}

@@

\Appendix

\begin{table*}[t]
\begin{center}
\begin{tabular}{ r  l  l  l  l  l  l}  
 \hline
 Operation & Kernel & Strides & Output Shape & BN & Dropout & Activation \\ 
 \hline
 G(\textbf{z}): Input \textbf{z} $\sim$ Normal(0,0.02) & N/A & N/A & (100,) & \ding{55} & 0 & N/A \\  
 Dense & N/A & N/A & (32768,) & \ding{55} & 0 & ReLU \\  
 Class input c & N/A & N/A & (1,) & \ding{55} & 0 & N/A \\
 Embedding & N/A & N/A & (1, 120) & \ding{55} & 0 & N/A \\
 Dense & N/A & N/A & (1,128) & \ding{55} & 0 & ReLU \\ 
 Reshape \textbf{z} & N/A & N/A & (128, 256) & \ding{55} & 0 & N/A \\
 Reshape c & N/A & N/A & (128, 1) & \ding{55} & 0 & N/A \\
 Concatenate & N/A & N/A & (128, 257) & \ding{55} & 0 & N/A \\
 Reshape & N/A & N/A & (64, 514) & \ding{55} & 0 & N/A \\
 Transposed Convolution & 18x1 & 2 & (256, 256) & \ding{51} & 0 & ReLU\\
 Transposed Convolution & 18x1 & 2 & (512, 128) & \ding{55} & 0 & ReLU\\
 Transposed Convolution & 18x1 & 2 & (1024, 64) & \ding{55} & 0 & ReLU\\
 Convolution & 18x1 & 1 & (1024, 1) & \ding{55} & 0 & Tanh \\
 Sky input & N/A & N/A & (3,) & \ding{55} & 0 & N/A \\
 Concatenate & N/A & N/A & (1027,) &  \ding{55} & 0 & N/A \\
 Lambda & N/A & N/A & (1024, 2) & \ding{55} & 0 & N/A \\
 D(\textbf{x}): Input \textbf{x} & N/A & N/A & (1024, 2) & \ding{55} & 0 & N/A \\
 Convolution & 14x1 & 2 & (512, 64) & \ding{55} & 0.5 & Leaky ReLU \\
 Convolution & 14x1 & 2 & (256, 128) & \ding{55} & 0.5 & Leaky ReLU \\
 Convolution & 14x1 & 2 & (128, 256) & \ding{55} & 0.5 & Leaky ReLU \\
 Convolution & 14x1 & 2 & (64, 512) & \ding{55} & 0.5 & Leaky ReLU \\
 Flatten & N/A & N/A & (32768,) & \ding{55} & 0 & N/A \\
 Dense & N/A & N/A & (1,) & \ding{55} & 0 & Sigmoid \\
 Dense & N/A & N/A & (5,) & \ding{55} & 0 & Softmax \\
 \hline
 Optimizer & \multicolumn{6}{l}{Adam($\alpha$ = 0.0002, $\beta_{1}$ = 0.5)} \\
 Batch size & \multicolumn{6}{l}{100}  \\
 Iterations & \multicolumn{6}{l}{60000}  \\
 Leaky ReLU slope & \multicolumn{6}{l}{0.2} \\
 Weight initialization & \multicolumn{6}{l}{Gaussian($\mu$ = 0, $\sigma$ = 0.02)} \\
 Generator loss & \multicolumn{6}{l}{Binary cross-entropy} \\
 Discriminator loss & \multicolumn{6}{l}{Binary cross-entropy \& sparse categorical cross-entropy} \\ 
 \hline
\end{tabular}
\end{center}
\end{table*}
